### 2017-10-31 submission/supplemental.Rmd
add table s4

colnames(table_s3) <- c("F statistic", "R2", "P-value", "Study", "Carcinoma n", "Control n")

@@

@@

**Table S4: Summary of Adenoma based on Surgery Received**

```{r supplemental_table5, echo=FALSE, message=FALSE, warning=FALSE}

>>>>

colnames(table_s3) <- c("F statistic", "R2", "P-value", "Study", "Adenoma n", "Control n")

@@

**Table S4: Bray-Curtis Distance Matrix Analyzed by PERMANOVA for Tissue Carcinoma**

```{r supplemental_table4, echo=FALSE, message=FALSE, warning=FALSE}

temp_t4a <- read_csv("../data/process/tables/beta_perm_unmatched_tissue_summary.csv")
temp_t4b <- read_csv("../data/process/tables/beta_perm_matched_tissue_summary.csv")

table_s4 <- temp_t4a %>% 
  bind_rows(temp_t4b) %>% 
  mutate(fstat = round(fstat, digits = 2), 
         r2 = round(r2, digits = 3), 
         pvalue = round(pvalue, digits = 4), 
         study = c("Sanapareddy", "Burns", "Flemer", "Chen", 
                   "Dejea (Matched)", "Geng (Matched)", "Burns (Matched)"))

colnames(table_s4) <- c("F statistic", "R2", "P-value", "Study", "Carcinoma n", "Control n")

kable(table_s4, format = "markdown", align = 'c', padding = 2)

@@
